---
title: "Mutual-Funds-Analysis"
author: "Lianna Novitz"
date: "4/16/2018"
output: html_document
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(gridExtra)
library(GGally) 
library(leaps) 
library(glmnet)
```

```{r}
Experience <- read_csv("/Users/lnovitz/Documents/Lianna's Projects/Git/R/Mutual-Funds-Kaggle-Data/mutual-funds/Experience.csv")
```
Data Exploration: Quick Look
```{r}
head(Experience)
summary(Experience)
names(Experience)
colnames(Experience)
colnames(Experience)[2] <- "Morningstar_Category"
colnames(Experience)[22] <- "Net_Flows"
```

Data Exploration: Counts
```{r}
Experience %>%
  group_by(Morningstar_Category) %>%
  count() %>% 
  arrange(desc(n))
```
Data Exploration: Visualization
```{r}
#ggplots
Experience %>% 
  select(c(1:22)) %>% #select 1:9 = the variables. always include predictor!
  ggpairs()
```

```{r}
#histogram
ggplot(Experience, 
       aes(x=Net_Flows)) +
  geom_histogram()
```
```{r}
#density plot
Experience %>%
ggplot(aes(x=Net_Flows)) +
  geom_density()
```
```{r}
#relationship btwn 2 vars
ggplot(Experience, 
       aes(y=Net_Flows, x=Investment)) +
  geom_point() +
  geom_smooth(method="lm")
```
#another density plot
```{r}
Experience %>% 
  ggplot(aes(x=Net_Flows, fill=factor(Investment))) +
  geom_density(alpha=.5)
```

#boxplot
```{r}
Experience %>% 
  ggplot(aes(x=factor(Investment), y='Net Flow')) +
  geom_boxplot()
```

#name a plot
garareaP <-
house_data %>% 
  ggplot(aes(x=GarageArea, y=SalePrice)) +
  geom_point()

#arrange plots
grid.arrange(qualP, buildyearP, remodyearP, bsmtsfP, airP, electricP, firstflrsfP, grlivareaP, bathP, rmsabvgrdP, garcarsP, garareaP,  ncol = 4, newpage = TRUE)


Linear Model
```{r}
#fit the model
model_1 <- lm(NetFlow ~ Investment, data = Experience)
#obtain a model summary
summary(model_1)
```

Logistic Model (binary response)
```{r}
log.big <- glm(Class ~ Adhes + BNucl + Chrom + Thick,
               data=wbca, family = binomial(link = "logit"))
summary(log.big)
predict(log.big, type = "response", 
        newdata = data.frame(Adhes=2, BNucl=2, Chrom = 2, Thick = 2))
```

Validation/Training
```{r}
set.seed(399)

House.subset <- 
  newhouse_data %>% 
  mutate(grp = sample(0:1, 
                      size=n(), 
                      replace=TRUE))

training <- House.subset %>% filter(grp == 0)
validation <- House.subset %>% filter(grp == 1)
```

Forward Selection and Cross Validation
```{r}
bestmods <- regsubsets(x = SalePrice ~ OverallQual + YearBuilt + YearRemodAdd + TotalBsmtSF + CentralAir + factor(Electrical) + FirstFlrSF + GrLivArea + factor(FullBath) + factor(TotRmsAbvGrd) + factor(GarageCars) + GarageArea,             
                   data = training %>% 
                     select(-grp),     
                   nvmax = 11,          
                   method = "forward") 
```

```{r}
predict.regsubsets <- function(object, newdata, id, ...){
  form <- as.formula(object$call[[2]])
  coefi <- coef(object, id=id)
  model.matrix(form, data=newdata)[,names(coefi)] %*% coefi
}
```

```{r}
vars = 12
mspeall = c()
for (i in 1:vars){
predict.regsubsets(object = bestmods, 
                   newdata = validation,
                   id = i)
mspeall[1] = actual - pred  
}
  
```